### 2016-03-09 paper/paper.tex
wrote results and conclusion sections

\section{FUTURE WORK \& CONCLUSION}

>>>>

For our final evaluation we made 20 runs of our learning process with 15
iterations each generating $25 \cdot 100 = 2500$ samples per iteration. Using
an Haswell Quad Core with 3.4GHz per core each iteration took about 3 minutes,
so the total runtime for each policy was about 45 minutes.

The policies start of only being able to push the object when the kilobots start
to the left of the object. After about 5 iterations they can also handle kilobot
starting positions above and below the object by first moving the kilobots to
the left and down and then pushing the object from the left side. After further
iterations the policies are able to push the object to the right even if the
kilobots start above and to the right of the object (see
\autoref{fig:policyEvolution}). With even more iterations the kilobot starting
positions from which the object can be pushed tend to extend even further, but
this improvement is inconsistent and the policies may even get worse again.
Therefore we manually inspected the policies at each iteration and choose a good
policy (which is typically found in the first about 15 iterations) for solving
the maze.

\begin{figure*}[!htb]
	\centering
	\subfloat[1 iterations]{
        \def\svgwidth{0.45\textwidth}
        \input{figures/policy_1.pdf_tex}
    }
    \hfill
	\subfloat[5 iterations]{
        \def\svgwidth{0.45\textwidth}
        \input{figures/policy_5.pdf_tex}
    }
    \hfill
	\subfloat[10 iterations]{
        \def\svgwidth{0.45\textwidth}
        \input{figures/policy_10.pdf_tex}
    }
    \hfill
	\subfloat[15 iterations]{
        \def\svgwidth{0.45\textwidth}
        \input{figures/policy_15.pdf_tex}
    }
    \hfill
	\caption[foo]{Evolution of the learned policy.}
	\label{fig:policyEvolution}
\end{figure*}

The value function also shows that kilobot positions left of the object are
preferrable to positions to the right and you can also somewhat see the value
function increasing when moving around the object from the right to the left
(see \autoref{fig:value}).

\begin{figure}[!htb]
	\centering
    \def\svgwidth{\columnwidth}
    \input{figures/value.pdf_tex}
    \caption{Learned value function after 8 iterations. The object (not shown
             here) is at the middle of the image.}
	\label{fig:value}
\end{figure}

With improving policies the object can be pushed to the right from a larger
number of kilobot starting positions and therefore the reward tends to increase
(see \autoref{fig:meanReward}).

\begin{figure}[!htb]
    \centering
    \resizebox{\linewidth}{!}{\input{figures/reward.tex}}
    \caption{Total reward for each iterations averaged over 8 runs.
             TODO: 20 runs are not complete yet}
    \label{fig:meanReward}
\end{figure}

We made the policy plots by getting the mean action for states distributed on a
grid and plotting it as an arrow indicating the direction the light should move
in. For this we set the relative light positions to evenly spaced values between
$-0.25$ and $0.25$ for the $x-$ and $y-$dimension and set the position for all
kilobots to coincide with the light position.

To compute the Value-function we use the same states and uniformly sample a
number of actions at random for each state. Then we compute the Q-values for all
state-action pairs and average them for each state.

To evaluate our policies we used our simulator to push the object through the
maze as described in \ref{sec:simulator}. We found that our learned policies are
sufficient to achieve this task and are even able to move the object when the
kilobots are (almost) completely on the wrong side which requires moving them
around the object. Moreover we can transfer our policy to more or less kilobots
and are still able to push the object because of our choice of kernel. We
learned the policy with 4 kilobots and testes it with 1,2,3,4,6,8 and 10
kilobots and it was able to push the object through the maze in each case.
Finally we were also able to push a circel through the maze even though the
policy was learned on a square.

\section{CONCLUSION \& FUTURE WORK}

In our experiments we achieved our goal to learn a policy to push an object
using multiple kilobots controlled by a single light and to combine this policy
with a maze solving policy to push the object through a maze. Our policy is also
transferable to a different number of kilobots and may be used to push objects of
different simple symmetric shapes which we tested for a circle.

Although this policy works well in the simulator it is not directly applicable
to the real kilobots because our simulator is overly simplistic. It moves
the kilobots directly toward the light instead of using phototaxis and also
allows for arbitrary light movements where in reality the light would be moved
by a robot arm which has some constraints on the forces used to move it.

Therefore a future work could simulate the kilobots more realistically and try
to transfer the learned policy to the real kilobots by building a maze and
controlling a robot arm holding a flaslight usign the learned policy.
